[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-22 analysis/paper.Rmd
Fixed typos, added missing figure.

There is a crisis of reproducibility and replication in the data science field. In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].  This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium. This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality]. While the first paper draws a connection between happiness and income, the second calls in the question the data used for this conclusion, and pulls in additional data for analysis. This second analysis, focused on the relationship between marriage and happiness, is the subject of replication in this paper.

@@

In this replication paper, three artifacts from the paper[@data] were reproduced. The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.

@@

The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and happiness. Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.

>>>>

There is a crisis of reproducibility and replication in the data science field. In an attempt to bolster confidence in scientific results, the following paper is a replication of "Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)" [@marriagehappiness].  This paper follows the ReScience replication method[@rescience] which strongly encourages open source practices as underlined by the format of this project: a github compendium. This particular replication is unique in that the paper being replicated is an alternate implementation of the paper:"Income Inequality and Happiness" [@incomeinequality]. While the first paper draws a connection between happiness and income, the second calls into question the data used to obtain the results stated, and pulls in additional data to re-assess the analysis. This second analysis, which focused on the relationship between marriage and happiness, is the subject of replication in this paper.

@@

In this replication paper, three artifacts from [@data] were reproduced. The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.

@@

The R function cor.test() was used to get the Pearson correlation coefficient between the different independent variables (income, age, sex, white, married) and the response variable, happiness. Grundberg et al.'s code was slightly modified to keep the same encoding of variables given the new dataset input.
